\documentclass{article}

% --- PACKAGES ---
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[
    a4paper,
    margin=1in
]{geometry}
\usepackage{parskip}
\usepackage{sectsty}
\usepackage{amsmath}

% --- DOCUMENT INFORMATION ---
\title{Autonomous MicroMouse Robot}
\author{Elman Steve Laguna}
\date{\today}

% --- COMMANDS to prevent page breaks ---
\sectionfont{\nopagebreak}
\subsectionfont{\nopagebreak}
\subsubsectionfont{\nopagebreak}
\widowpenalty=10000
\clubpenalty=10000

\begin{document}

\maketitle

\include{reintroduction}

\include{map_generation}

\include{path_finding}
\include{issues}

\begin{thebibliography}{9}

% --- Academic Paper ---
\bibitem{slam_review}
M. Aborizky, H. A. As’ari, A. Fadlil and R. D. P. W. "Lidar-Based 2D SLAM for Mobile Robot in an Indoor Environment: A Review," \textit{2021 9th International Conference on Information and Communication Technology (ICoICT)}, 2021, pp. 488-493. doi: 10.1109/ICoICT52021.2021.9538731.

% --- Web Articles & Tutorials ---
\bibitem{raycasting_tutorial}
L. Vandevenne, "Raycasting," \textit{Lode's Computer Graphics Tutorial}. [Online]. Available: \url{https://lodev.org/cgtutor/raycasting.html}

\bibitem{lidar_basics}
NEON Science, "Lidar Basics," \textit{National Ecological Observatory Network}, 2021. [Online]. Available: \url{https://www.neonscience.org/resources/learning-hub/tutorials/lidar-basics}

\bibitem{line_intersection}
Zona Land Education, "Intersection of Two Lines," \textit{Zona Land Education}. [Online]. Available: \url{http://zonalandeducation.com/mmts/intersections/intersectionOfTwoLines1/intersectionOfTwoLines1.html}

% --- Videos ---
\bibitem{lidar_video}
NEON Science, "How Does LiDAR Remote Sensing Work? Light Detection and Ranging," \textit{YouTube}, Nov. 24, 2014. [Video]. Available: \url{https://www.youtube.com/watch?v=EYbhNSUnIdU}

\bibitem{pygame_raycast_video}
FinFET, "Raycasting with Pygame in Python! Simple 3D game tutorial Devlog," \textit{YouTube}, Nov. 6, 2021. [Video]. Available: \url{https://www.youtube.com/watch?v=4gqPv7A_YRY}

\bibitem{raycast_explained_video}
WeirdDevers, "Ray casting fully explained. Pseudo 3D game," \textit{YouTube}, Dec. 27, 2020. [Video]. Available: \url{https://www.youtube.com/watch?v=g8p7nAbDz6Y}

\bibitem{maze_solving_competition_video}
Veritasium, "The Fastest Maze-Solving Competition On Earth," \textit{YouTube}, May 24, 2023. [Video]. Available: \url{https://www.youtube.com/watch?v=ZMQbHMgK2rw}

\bibitem{mazes_school_video}
mattbatwings, "What School Didn't Tell You About Mazes \#SoMEpi," \textit{YouTube}, Jun. 22, 2024. [Video]. Available: \url{https://www.youtube.com/watch?v=uctN47p_KVk}

\bibitem{slam_robot_video}
Kai Nakamura, "How to Make an Autonomous Mapping Robot Using SLAM," \textit{YouTube}, May 14, 2024. [Video]. Available: \url{https://www.youtube.com/watch?v=xqjVTE7QvOg}

\bibitem{lidar_ros_video}
Articulated Robotics, "How do we add LIDAR to a ROS robot?," \textit{YouTube}, Jun. 2, 2022. [Video]. Available: \url{https://www.youtube.com/watch?v=eJZXRncGaGM}

\end{thebibliography}

\end{document}